\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-10-14 doc/flexiblesusy-paper.tex
expand undefined TeX macros

The low-scale constraint matches the SUSY model to the Standard Model.
Currently \fs allows only SUSY models with semisimple gauge groups,
which contain the Standard Model gauge group $\SUc\times\SUL\times\UY$
as factor.  This enables \fs to directly identify the strong,
left-handed and hypercharge gauge couplings $g_i$ ($i=1,2,3$).

>>>>

The low-scale constraint matches the SUSY model to the Standard Model.
Currently \fs allows only SUSY models with semisimple gauge groups,
which contain the Standard Model gauge group $SU(3)\times SU(2)\times
U(1)$ as factor.  This enables \fs to directly identify the strong,
left-handed and hypercharge gauge couplings $g_i$ ($i=1,2,3$).
